**First high-frequency time series of carbonate chemistry in the Arctic**

### 2022-03-30 awipev-CO2_presentation.Rmd
new slides + format

---
title: "**First high-frequency time series of carbonate chemistry in the Arctic**" 
author: "**Jean-Pierre Gattuso**^1,2^ and Samir Alliouane^1^ and Philipp Fisher^3^"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document:
    # code_folding: show
#    css: acid.css
    fig_caption: yes
    fig_width: 2
    fig_height: 2
    highlight: default    
    number_sections: no
    theme: yeti
    toc: no
    toc_float: no
fontsize: 32pt
language: Australian
#css: acid.css
## mainfont: PT Serif  
## monofont: PT Mono
#csl: frontiers.csl
## sansfont: PT Sans
#bibliography: ArcticKelp.bib
## papersize: A4
---
<!-- <style type="text/css"> -->
<!-- .main-container { -->
<!--   max-width: 100% !important; -->
<!--   margin: auto; -->
<!-- } -->
</style>
<style type="text/css">
.main-container {
  max-width: 100% !important;
  margin: auto;
}
body{
  font-size: 24pt;
}
h1,h2,h3,h4,h5,h6{
  font-size: 32pt;
}
</style>

@@

Fransner et al. (2022)
![ ](images/map_fransner.png){width="50%"}
![ ](images/pH_fransner.png)

@@

## **Instruments in the FerryBox**
![ ](images/container.png)

![ ](images/intake.png)

![ ](images/ferrybox.jpg)

@@

## No longer in real-time: https://awipev-co2.obs-vlfr.fr
![ ](images/web_page.png)

@@

## **Availability of data**
:::: {style="display: flex;"}
::: {class='col-md-4'}
Many challenges:

@@

## **Nutrients**
:::: {style="display: flex;"}
::: {class='col-md-4'}

@@

## **K1 and K2**

@@

## **Total alkalinity vs salinity relationship**
![ ](figures/p_at_s.png)

@@

## **Time series of key variables**
![ ](figures/time_series.png)

@@

## **Monthly means**
![ ](figures/ts_boxplots.png)

@@

## **Consistency**

::: {style="text-align:center" markdown="1"}
![ ](figures/pco2_calc_meas.png)
:::

@@

## **Water column stratification**

@@

@@

- **First** high-frequency time series of the carbonate system in the Arctic 
- **Positive aspects**: 
  - Excellent support from AWIPEV staff but work overload
  - IPEV support secured for another 4-year period (2019-2022)
- **Logistical difficulties**:
  - Challenging environment; divers needed to sort out issues
  - Difficult and costly to gather a team and organize field trip at short notice
  - Winter sampling essential (once a month this season, more frequently would be more desirable)
  - Demanding for AWIPEV staff
  - IPEV does not cover the cost of analyses required for calibration (ca. 1000 €)

>>>>

---
title: "**First high-frequency time series of carbonate chemistry in the Arctic**" 
author: "Jean-Pierre Gattuso^1,2^ and Samir Alliouane^1^ and Philipp Fisher^3^"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document:
    # code_folding: show
#    css: acid.css
    fig_caption: no
    #fig_width: 2
    #fig_height: 2
    highlight: default    
    number_sections: no
    #theme: yeti
    theme: cerulean
    toc: no
    toc_float: no
fontsize: 32pt
#language: Australian
#css: acid.css
## mainfont: PT Serif  
## monofont: PT Mono
#csl: frontiers.csl
## sansfont: PT Sans
#bibliography: ArcticKelp.bib
## papersize: A4
---
<!-- <style type="text/css"> -->
<!-- .main-container { -->
<!--   max-width: 100% !important; -->
<!--   margin: auto; -->
<!-- } -->
</style>
<style type="text/css">
.main-container {
  max-width: 100% !important;
  margin: auto;
}
body{
  font-size: 24pt;
}
h1,h2,h3,h4,h5,h6{
  font-size: 32pt;
}
</style>

@@

Fransner et al. (2022)

![ ](images/map_fransner.png){width="50%"}
![ ](images/pH_fransner.png){width="50%"}

@@

## **Instruments in the FerryBox**
![ ](images/container.png){width="50%"}

![ ](images/intake.png){width="50%"}

![ ](images/ferrybox.jpg){width="50%"}

@@

# No longer in real-time: https://awipev-co2.obs-vlfr.fr
![ ](images/web_page.png)

@@

# **Availability of data**
:::: {style="display: flex;"}
::: {class='col-md-4'}
Many challenges:

@@

# **Nutrients**
:::: {style="display: flex;"}
::: {class='col-md-4'}

@@

# **K1 and K2**

@@

# **Total alkalinity vs salinity relationship**
![ ](figures/p_at_s.png)

@@

# **Time series of key variables**
![ ](figures/time_series.png)

@@

# **Monthly means**
![ ](figures/ts_boxplots.png)

@@

# **Consistency**

<!-- ::: {style="text-align:center" markdown="1"} -->
![ ](figures/pco2_calc_meas.png)
<!-- ::: -->

@@

# **Water column stratification**

@@

# **Air-sea CO<sub>2</sub> flux**

  ![ ](figures/air-sea_CO2_flux.png)

@@

- **Positive aspects**: 
  - **First** high-frequency time series of the carbonate system in the Arctic 
  - Excellent support from AWIPEV staff until 2020
- **Logistical difficulties**:
  - Challenging environment; divers needed to sort out issues
  - Difficult and costly to gather a team and organize field trip at short notice
  - Winter sampling essential (once a month this season, more frequently would be more desirable)
  - IPEV does not cover the cost of analyses required for calibration (ca. 1000 €)

# **Acknowledgements**

- AWIPEV staff until 2020
- Numerous AWI divers
- SNAPO-CO2
- Willem H. van de Poll who provided nutrient data
- Coastal Observing System for Northern and Arctic Seas (COSYNA)
- Helmholtz large-scale infrastructure projects ACROSS and MOSES
- French Polar Institute (IPEV) 
- EU projects Jericho-Next, INTAROS and FACE-IT
- Ove Hermansen, Cathrine Lund Myhre, and Stephen Platt at Norwegian institute for air research (NILU) for their assistance with atmospheric CO2 data from the Zeppelin observatory, as well as the Integrated Carbon Observing System (ICOS)-Norway, Norwegian Research Council project NFR-207587, and the Norwegian Environment Agency
